---
title: "Internal Assessment"
author: "ECON03SEC1 2023"
format: html
editor_options: 
  chunk_output_type: console
---

## Use the gapminder dataset to answer the following questions:
1. How many unique countries are included in the dataset? 
```{r}
library(gapminder)
names(gapminder)
library(tidyverse)
unique(gapminder$country)
```


2. Identify the countries with the highest and lowest GDP per capita. 
```{r}
gapminder %>% 
  arrange(gdpPercap) %>% 
  select(country, gdpPercap)

gapminder %>% 
  arrange(desc(gdpPercap)) %>% 
  select(country, gdpPercap)

```


3. Calculate the average life expectancy across all countries and years.
```{r}
gapminder %>% 
  group_by(country, year) %>% 
  summarise(mean(lifeExp))
```


4. Create a box plot to visualize the distribution of GDP per capita for each continent. Write down your observations.
```{r}
gapminder %>% 
  ggplot(aes(x = continent, y = gdpPercap))+
  geom_boxplot()
```

5. Calculate the correlation between life expectancy and GDP per capita for each continent over the years 1952 to 2007. What are your observations?
```{r}
gapminder %>% 
  group_by(continent, year) %>% 
  summarise(cor(lifeExp, gdpPercap)) 
```

6. Create histograms or density plots to visualize the distribution of life expectancy, GDP per capita, and population size. 
7. Create scatter plots to examine the relationship between GDP per capita and life expectancy continent wise. (Use log of GDP per capita and log life expectancy).
8. Plot a line graph to show the change in life expectancy and GDP per capita for a specific country over time.  (Use log of GDP per capita and log life expectancy).
```{r}
gapminder %>% 
  filter(country == "India") %>% 
  ggplot(aes(x = year))+
  geom_line(aes(y = log(lifeExp)), col = "red")+
  geom_line(aes(y = log(gdpPercap)))
```

